Spin canonical divisors of log stacky curves

### 2015-06-29 stacky_write_up/spin_cring.tex
g0 base case ordering switch

\todo{do this part}
Part on Kodaira--Spencer \cite{kodaira:complex-manifolds}.
Use \cite[Lemma 10.2.1]{vzb:stacky} to obtain the desired translation to algebraic 
geometry.

@@

We can directly see that the relations are given in degrees $10$
and $14$. In particular, we have relations
\begin{align*}
	&a_1 x_{5, 1}^2 + a_2 x_{3, 1} x_{7, 1} + a_3 x_{3, 1} x_{7, 2} = 
	0 &\text{ in degree $10$} \\
	&b_1 x_{7, 1}^2 + b_2 x_{3, 1}^3 x_{5, 1} + b_3 x_{7, 1} x_{7, 2} 
	+ b_4 x_{7, 2}^2 = 0  &\text{ in degree $14$}
\end{align*}

\noindent
and note that $a_1$ and $b_1$ are both nonzero. If $a_1 = 0$, then we
have that
\[
	a_2 x_{3, 1} x_{7, 1} = a_3 x_{3, 1} x_{7, 2}
\]

\noindent
However, $x_{3, 1} x_{7, 1}$ has pole orders $(3, 4, 3)$ and
$x_{3, 1} x_{7, 2}$ has pole orders $(3, 3, 4)$ so their
coefficients must be zero for this equality to hold. We have a
similar pole-order consideration in forcing $b_1$ to be nonzero.

Let $I$ be the ideal generated by these relations in
$k[x_{7, 1}, x_{7, 2}, x_{5, 1}, x_{3, 1}]$. Under grlex with
$x_{7,1} \prec x_{7,2} \prec x_{5,1} \prec x_{3,1}$, the initial
ideal of $I$ is
\[
	in_\prec(I) = \langle x_{5, 1}^2, x_{7, 1}^2 \rangle
\]

>>>>

\todo{do this part}
Part on Kodaira--Spencer \cite{kodaira:complex-manifolds}.

@@

We can directly see that the relations are given in degrees $10$
and $14$. In particular, we have relations
\begin{align*}
	&a_1 x_{3, 1} x_{7, 2} + a_2 x_{3, 1} x_{7, 1} + a_3 x_{5, 1}^2 = 
	0 &\text{ in degree $10$} \\
	&b_1 x_{7, 2}^2 + b_2 x_{7, 1} x_{7, 2} + b_3 x_{7, 1}^2
	+ b_4 x_{3, 1}^3 x_{5, 1} = 0  &\text{ in degree $14$}
\end{align*}

\noindent
and note that $a_1$ and $b_1$ are both nonzero. If $a_1 = 0$, then we
have that
\[
	a_2 x_{3, 1} x_{7, 1} = -a_3 x_{5, 1}^2
\]

\noindent
However, $x_{3, 1} x_{7, 1}$ has pole orders $(3, 4, 3)$ and
$x_{5, 1}^2$ has pole orders $(2, 4, 4)$ so their
coefficients must be zero for this equality to hold. We have a
similar pole order consideration in forcing $b_1$ to be nonzero.

Let $I$ be the ideal generated by these relations in
$k[x_{7, 1}, x_{7, 2}, x_{5, 1}, x_{3, 1}]$. Under grlex with
$x_{3,1} \prec x_{5,1} \prec x_{7,1} \prec x_{7,2}$, the initial
ideal of $I$ is
\[
	in_\prec(I) = \langle x_{3, 1} x_{7, 2}, x_{7, 2}^2 \rangle
\]
